POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2023-07-13 challenges.tex
Clarify that linearity is also necessary for other things than just session types.
Add some motivation for explicitly reasoning about scope extrusion to the challenge description in the appendix.

This challenge formalises a proof that requires reasoning about linearity of channels.
Linearity is the notion that a channel must be used exactly once in a process.
This is necessary to prove properties about session type systems.

@@

>>>>

This challenge formalises a proof that requires reasoning about linearity of channels.
Linearity is the notion that a channel must be used exactly once in a process.
This is necessary to prove properties about session type systems.
Linear reasoning is also necessary to formalise e.g.\ linear and affine types for the pi-calculus and cut elimination in linear logics.

@@

Reasoning about scope extrusion explicitly can sometimes be avoided by introducing a structural congruence rule into the semantics, but doing this means we lose information about the scope when reasoning about the semantics.
Explicitly reasoning about scope extrusion is necessary to describe e.g.\ monitors and compositions.
